Embedding Intuitionistic into Classical Logic

### 2022-07-14 CSL/lipics-v2021-EIICL.tex
Restructuring

We end up with the following translation:

\begin{theorem}\label{fullFOtranslation}
	Let $\mathcal S$ be as above and $\mathcal F_\to\subseteq\mathcal S$ contain formulas of the form $\forall \vec t((A(\vec z_A)\to B(\vec z_B))\to C(\vec z_C))$ and $\mathcal F_\forall\subseteq\mathcal S$ the formulas of the form $\forall \vec z(\forall xA(\vec z_A)\to B(\vec z_B))$. Let $\mathcal F = \mathcal F_\to\cup\mathcal F_\forall$. For every $n$-ary atomic relation $R$ define a new $n+1$-ary relation $R^\#$. For every $\psi\in\mathcal F$ define a new function symbol $f_\psi$. Consider a new binary relation symbol $E$ and define $\vec E(\vec x, u) := \bigwedge\{E(x, u)\:|\:x\in\vec x\}$. Obtain $\mathcal S^\#$ by including formulas as follows:
	\begin{itemize}
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\to (B^\#(\vec b, u)\circ C^\#(\vec c, u))))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z(A(\vec a)\to (B(\vec b)\circ C(\vec c)))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\circ B^\#(\vec b, u))\to C^\#(\vec c, u))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z((A(\vec a)\circ B(\vec b))\to C(\vec c))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to(A^\#(\vec a, f(\vec z, u))\to B^\#(\vec b, f(\vec z, u)))\to C^\#(\vec c, u))$ for each $\psi = \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c))\in\mathcal S$
		\item  $\forall \vec z\forall u(\vec E(\vec z, u)\to \forall x(E(x, f(\vec z, u))\to A^\#(\vec a, f(\vec z, u)))\to B^\#(\vec b, u))$\\for each $\forall \vec z(\forall xA(\vec a)\to B(\vec t_B))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec a, u)\to \forall x(E(x, u)\to B^\#(\vec b, u)))$\\for each $\forall \vec t(A(\vec a)\to \forall xB(\vec b))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to \exists x(E(x, u)\wedge A^\#(\vec z, u))\to B^\#(\vec b))$\\for each $\forall \vec z(\exists xA(\vec a)\to B(\vec b))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec b)\to \exists x(E(x, u)\wedge B^\#(\vec b, u)))$\\for each $\forall \vec z(A(\vec a)\to \exists xB(\vec b))\in\mathcal S$
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically iff $\exists xE(x, s)\to K\to \bigwedge\mathcal S^\#\to P^\#(s)$ is classically valid, where $s$ is a new constant symbol, $\Sigma$ is the original signature and
	\begin{align*}
		K := &\:\bigwedge\{\forall x\forall u((E(x, u)\to E(x, f_\psi(u)))\:|\:\psi\in\mathcal F\}\wedge\\
		&\:\forall u\left(\exists xE(x, u)\to \bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f$ is a function symbol in $\Sigma$}\}\right)\wedge\\
		&\:\bigwedge\{\forall\vec z_1\forall \vec z_2\forall u(A^\#(\vec z_1, u)\to A^\#(\vec z_1, f_\psi(\vec z_2, u)))\:|\:\text{$\psi\in\mathcal F$, $A$ is a relation symbol in $\Sigma$}\}
	\end{align*}
	The size of the obtained formula is linear in the input. However a $|\mathcal F| + 1$ new function symbols and the new binary predicate $E$ were introduced and each $n$-ary relation symbol has been extended to a $n+1$-ary relation symbol.
\end{theorem}

@@

\begin{definition}
	A \emph{valuation} $v$ is a function that assigns to each propositional variable $A$ a \textbf{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$
		\item $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ and $v\models\psi$.
	\end{itemize}
	$v$ is a \textbf{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC}.
\end{definition}

@@

@@

We are now ready to put everything together. Recall that our goal is for a formula to give a modified formula that is valid classically iff the original formula is valid intuitionistically. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi$$

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$

where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u)$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A_\psi(l)\to B_\psi(l))\to C_\psi(k)))$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\vee (B_\psi(k))\to C_\psi(k)))$$
$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
and $f$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and
$$f_\psi^{I'}(u) = \begin{cases}
	f^I_\psi(u)&\text{ iff $u\preceq f^{I}_\psi(u)$}\\
	u&\text{ else}
\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\forall k(A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k((A_\psi(k)\wedge B_\psi(k))\to C_\psi(k))$$
$$\forall k(A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k((A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
$$\forall k((A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

\begin{proof}
	1. If $C_\psi^I(u)$ is true then we are done due to persistency. Otherwise we know that $(A_\psi^I(f_\psi^I(u))\to B_\psi^I(f_\psi^I(u)))\to C_\psi^I(f_\psi^I(u))$ holds, so $A_\psi^I(f_\psi^I(u))\to B_\psi^I(f_\psi^I(u))$ must be true.

	2. If $C_\psi^I(u)$ is true then $C_\psi^I(w)$ is also true and we are done. So suppose $A_\psi^I(u)\to B_\psi^I(u)$ is false, i.e. $A_\psi^I(u)$ true and $B_\psi^I(u)$ false. Then due to the persistency condition $A_\psi^I(w)$ is also true. Again if $C_\psi^I(w)$ is true we are done. Otherwise we know that $B^I(f^I_\psi(w))$ must be false, since $(A^I_\psi(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I_\psi(w)$ and $A^I_\psi(f^I_\psi(w))$ hold. But then due to persistency so is $B^I_\psi(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

@@

\begin{definition}
	Suppose $\mathcal S$ is a set of formulas $\psi$ of the form
	$$A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi),(A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$
	Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$ and $\Lambda$ the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ occurring in $\mathcal S$ and $k\in \mathcal F_\to$ consider a new atom $A^{k}$, which will correspond to $A^{I_F}(k)$ from the previous definition. Obtain $\mathcal S^\#$ by including the formulas
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k_\psi\to (B^k_\psi\circ C^k_\psi)$ for each $\circ\in\{\wedge,\vee\}$, $A_\psi\to (B_\psi\circ C_\psi)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k_\psi\circ B^k_\psi)\to C^k_\psi$ for each $\circ\in\{\wedge,\vee\}$, $A_\psi\to (B_\psi\circ C_\psi)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}_\psi\to B^{k\psi}_\psi)\to C^k_\psi$ for $(A_\psi\to B_\psi)\to C_\psi\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
\end{definition}

@@

Fix some set $\mathcal S$ of formulas $\psi$ of the form $$A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$and$$\varphi = \bigwedge \mathcal S\to P$$
and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is: Instead of expressing validity at every node of $\mathcal M_T$ - which was done in the CPC translation - we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition handle the branching, i.e. express which path is considered.

@@

$$\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),$$$$ \forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),
\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)),$$$$ \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),$$$$ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))$$	
As in the propositional case we will now encode the Kripke Semantics, this time not only the relation $\preceq$ but also $E$ has to be axiomatized. For that we use the following predicates:
\begin{itemize}
	\item PartialOrder($\preceq$) encoding that $\preceq$ is a partial order.
	\item DomainSubset$(u, w)$ encoding that the domain at $u$ is a subset of that at $w$.
	\item World($u$) encoding that $u$ represents a world.
	\item DomainClosed($u$) which encodes that at $u$ the domain is closed under functions, e.g. contains all interpretations of constants.
	\item Persistent$(u, w)$ which encodes that persistency is satisfied between $u$ and $w$, i.e. for all predicates $A$ and domain elements $x$ with $A(x)$ at $u$ we have $A(x)$ at $w$.
\end{itemize}
Then analogously to the predicate case define
\begin{align*}
	K(\varphi) = \:& \text{PartialOrder}(\preceq) \wedge \\
				 & \forall u \forall w (u\preceq w\to \text{DomainSubset}(u, w)) \wedge\\
				 & \forall u(\text{World(u)}\to \text{DomainClosed}(u))\wedge\\
				 & \forall u\forall w (u\preceq w\to \text{Persistent}(u, w))
\end{align*}
Example encodings could be
\begin{align*}
	\text{PartialOrder}(\preceq) = &\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
	\text{DomainSubset}(u, w) = &\:\forall z(E(z, u)\to E(z, w))\\
	\text{World}(u) = &\:\exists xE(x, u)\\
	\text{DomainClosed}(u) = &\:\bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f\in\Sigma$ is a function symbol}\}\\
	\text{Pesistent}(u, w) = &\:\bigwedge\{\forall\vec z(\vec A^\#(\vec z, u)\to A^\#(\vec z, w))\:|\:\text{$A\in\Sigma$ is a relation symbol}\}
\end{align*}

@@

Part 2 of this Lemma does not hold for $\psi\in\mathcal F_\forall$, because even if for all $x$ with $E(x, v$) we have $A(x, v)$ there could be some term $t$ with $\neg E(t, v)$ and $w$ with $v\preceq w$ such that $E(t, w)$ and $\neg A(t, w)$. This is why we must consider sequences that have repetitions of such formulas:

>>>>

\begin{theorem}
	There exists a linear-time procedure that gives for every first-order formula $\varphi$ a formula $\varphi^\#$ such that $\varphi$ is intuitionistically valid if and only if $\varphi^\#$ is classically valid. The size of $\varphi^\#$ is in linear in the size of $|\varphi|$, however for each $n$-ary relation symbol in $\varphi$ there is a corresponding $n+1$-ary relation symbol in $\varphi^\#$ and furthermore $\varphi$ contains a new binary predicate $E$ as well as a number of new function symbols. Furthermore there is an effective translation between intuitionistic counter-models of $\varphi$ and classical counter-models of $\varphi^\#$.
\end{theorem}
The complete translation is stated in Theorem~\ref{fullFOtranslation}.

@@

\begin{definition}
	A \emph{valuation} $v$ is a function that assigns to each propositional variable $A$ a \textbf{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$
		\item $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
	$v$ is a \textbf{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC}.
\end{definition}

@@

\section{IPC to simplified CQC}

We are now ready to put these two reduction together with our embedding f. Let $\varphi$ be some propositional formula. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi$$

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C$$

where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u)$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))$$
$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k)))$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))$$
$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k))$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and
$$f_\psi^{I'}(u) = \begin{cases}
	f^I_\psi(u)&\text{ iff $u\preceq f^{I}_\psi(u)$}\\
	u&\text{ else}
\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\forall k(A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k((A_\psi(k)\wedge B_\psi(k))\to C_\psi(k))$$
$$\forall k(A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k((A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
$$\forall k((A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

This is as far as the first-order encoding can be simplified. What remains is the elimination of the remaining weak $\forall$-quantifiers.

@@

@@

\begin{proof}
	1. If $C^I(u)$ is true then we are done due to persistency. Otherwise we know that $(A^I(f_\psi^I(u))\to B^I(f_\psi^I(u)))\to C^I(f_\psi^I(u))$ holds, so $A^I(f_\psi^I(u))\to B^I(f_\psi^I(u))$ must be true.

	2. If $C^I(u)$ is true then $C^I(w)$ is also true and we are done. So suppose $A^I(u)\to B^I(u)$ is false, i.e. $A^I(u)$ true and $B^I(u)$ false. Then due to the persistency condition $A^I(w)$ is also true. Again if $C^I(w)$ is true we are done. Otherwise we know that $B^I(f^I(w))$ must be false, since $(A^I(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I(w)$ and $A^I(f^I_\psi(w))$ hold. But then due to persistency so is $B^I(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

@@

\begin{definition}
	Suppose $\mathcal S$ is a set of formulas $\psi$ of the form
	$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C),(A\vee B)\to C, (A\to B)\to C$$
	Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$ and $\Lambda$ the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ occurring in $\mathcal S$ and $k\in \mathcal F_\to$ consider a new atom $A^{k}$, which will correspond to $A^{I_F}(k)$ from the previous definition. Obtain $\mathcal S^\#$ by including the formulas
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $(A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
\end{definition}

@@

Fix some set $\mathcal S$ of formulas $\psi$ of the form $$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C$$and$$\varphi = \bigwedge \mathcal S\to P$$
and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is: Instead of expressing validity at every node of $\mathcal M_T$ - which was done in the CPC translation - we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition handle the branching, i.e. express which path is considered.

@@

$$\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),$$$$ \forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),
\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)),$$$$ \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),$$$$ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))$$

The complete result that we will show is as follows:
\begin{theorem}\label{fullFOtranslation}
	Let $\mathcal S$ be as above and $\mathcal F_\to\subseteq\mathcal S$ contain the formulas of the form $\forall \vec t((A(\vec z_A)\to B(\vec z_B))\to C(\vec z_C))$ and $\mathcal F_\forall\subseteq\mathcal S$ the formulas of the form $\forall \vec z(\forall xA(\vec z_A)\to B(\vec z_B))$. Let $\mathcal F = \mathcal F_\to\cup\mathcal F_\forall$. For every $n$-ary atomic relation $R$ define a new $n+1$-ary relation $R^\#$. For every $\psi\in\mathcal F$ define a new function symbol $f_\psi$. Consider a new binary relation symbol $E$ and define $\vec E(\vec x, u) := \bigwedge\{E(x, u)\:|\:x\in\vec x\}$. Obtain $\mathcal S^\#$ by including formulas as follows:
	\begin{itemize}
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\to (B^\#(\vec b, u)\circ C^\#(\vec c, u))))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z(A(\vec a)\to (B(\vec b)\circ C(\vec c)))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\circ B^\#(\vec b, u))\to C^\#(\vec c, u))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z((A(\vec a)\circ B(\vec b))\to C(\vec c))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to(A^\#(\vec a, f(\vec z, u))\to B^\#(\vec b, f(\vec z, u)))\to C^\#(\vec c, u))$ for each $\psi = \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c))\in\mathcal S$
		\item  $\forall \vec z\forall u(\vec E(\vec z, u)\to \forall x(E(x, f(\vec z, u))\to A^\#(\vec a, f(\vec z, u)))\to B^\#(\vec b, u))$\\for each $\forall \vec z(\forall xA(\vec a)\to B(\vec t_B))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec a, u)\to \forall x(E(x, u)\to B^\#(\vec b, u)))$\\for each $\forall \vec t(A(\vec a)\to \forall xB(\vec b))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to \exists x(E(x, u)\wedge A^\#(\vec z, u))\to B^\#(\vec b))$\\for each $\forall \vec z(\exists xA(\vec a)\to B(\vec b))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec b)\to \exists x(E(x, u)\wedge B^\#(\vec b, u)))$\\for each $\forall \vec z(A(\vec a)\to \exists xB(\vec b))\in\mathcal S$
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically iff $\exists xE(x, s)\to K\to \bigwedge\mathcal S^\#\to P^\#(s)$ is classically valid, where $s$ is a new constant symbol, $\Sigma$ is the original signature and
	\begin{align*}
		K := &\:\bigwedge\{\forall x\forall u((E(x, u)\to E(x, f_\psi(u)))\:|\:\psi\in\mathcal F\}\wedge\\
		&\:\forall u\left(\exists xE(x, u)\to \bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f$ is a function symbol in $\Sigma$}\}\right)\wedge\\
		&\:\bigwedge\{\forall\vec z_1\forall \vec z_2\forall u(A^\#(\vec z_1, u)\to A^\#(\vec z_1, f_\psi(\vec z_2, u)))\:|\:\text{$\psi\in\mathcal F$, $A$ is a relation symbol in $\Sigma$}\}
	\end{align*}
	The size of the obtained formula is linear in the input. However a $|\mathcal F| + 1$ new function symbols and the new binary predicate $E$ were introduced and each $n$-ary relation symbol has been extended to a $n+1$-ary relation symbol.
\end{theorem}

It is not possible to completely eliminate worlds from the domain as in the propositional case, since counter-models possibly must be infinite. We will see why that is in more detail later.

\subsection{Encoding Kripke Semantics}

As in the propositional case we must encode the Kripke Semantics, this time not only the relation $\preceq$ but also $E$ has to be axiomatized. For that we use the following predicates:
\begin{itemize}
	\item PartialOrder($\preceq$) encoding that $\preceq$ is a partial order.
	\item DomainSubset$(u, w)$ encoding that the domain at $u$ is a subset of that at $w$.
	\item World($u$) encoding that $u$ represents a world.
	\item DomainClosed($u$) which encodes that at $u$ the domain is closed under functions, e.g. contains all interpretations of constants.
	\item Persistent$(u, w)$ which encodes that persistency is satisfied between $u$ and $w$, i.e. for all predicates $A$ and domain elements $x$ with $A(x)$ at $u$ we have $A(x)$ at $w$.
\end{itemize}
Then analogously to the predicate case define
\begin{align*}
	K(\varphi) = \:& \text{PartialOrder}(\preceq) \wedge \\
				 & \forall u \forall w (u\preceq w\to \text{DomainSubset}(u, w)) \wedge\\
				 & \forall u(\text{World(u)}\to \text{DomainClosed}(u))\wedge\\
				 & \forall u\forall w (u\preceq w\to \text{Persistent}(u, w))
\end{align*}
Example encodings could be
\begin{align*}
	\text{PartialOrder}(\preceq) = &\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
	\text{DomainSubset}(u, w) = &\:\forall z(E(z, u)\to E(z, w))\\
	\text{World}(u) = &\:\exists xE(x, u)\\
	\text{DomainClosed}(u) = &\:\bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f\in\Sigma$ is a function symbol}\}\\
	\text{Pesistent}(u, w) = &\:\bigwedge\{\forall\vec z(\vec A^\#(\vec z, u)\to A^\#(\vec z, w))\:|\:\text{$A\in\Sigma$ is a relation symbol}\}
\end{align*}

@@

However Part 2 of this Lemma does not hold for $\psi\in\mathcal F_\forall$, because even if for all $x$ with $E(x, v$) we have $A(x, v)$ there could be some term $t$ with $\neg E(t, v)$ and $w$ with $v\preceq w$ such that $E(t, w)$ and $\neg A(t, w)$. This is why we must consider sequences that have repetitions of such formulas:
